Empirical normative theories

### 2020-07-02 simple.tex
Rewrite clean until Empirical th; disc about ET

\section{Additive single-answer empirical theories}
\subsection{Definition}
\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
${\gbeats} \subseteq \allargs × \allargs$,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range equals ${\gbeatsinv}(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: ${\dbeatsinv}(\ar_1)$ is a singleton). 
Define $\df \subseteq \allargs × \alldargs$ as $\df = {\dbeatsinv} \circ {\gbeatsinv}$. 
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
As usual, $\ar + \ard$ means $+(\ar, \ard)$. 
Define $\dfp \subseteq \allargs × \allargs$ as, $\forall \ar \in \allargs$: $\dfp(\ar) = \ar + \df(\ar) = \set{\ar + \ard \suchthat \ard \in \df(\ar)}$.
An empirical theory must satisfy
$\forall \ar \in {\gleadsto}(\allargs): \exists k \in \N^* \suchthat \dfp^k(\ar) = \emptyset$.

\subsection{Falsifiability}
Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$.

Given $i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $d^{i, \phi}(\ar) \subseteq \alldargs$, as $d^{i, \phi}(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$. Define $d^{i, \phi}_+$ as $d^{i, \phi}_+(\ar) = \ar + d^{i, \phi}(\ar)$.
Given $i \in I, \phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $d^{i, \phi}_+$: $\gargs[i, \phi] = \cup_{k \in \N} (d^{i, \phi}_+)^k({\gleadstoinv}(\phi))$, where $(d^{i, \phi}_+)^0$ is the identity function.

@@

\begin{definition}[Convincingness]
	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \ar \in \gargs[i, \phi]: \ar$ $i$-defends $\phi$.
\end{definition}

A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × {\gleadsto}(\allargs) × \allhist$ such that $\exists \ar \in \histend \cap \gargs[i, \phi] \suchthat {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.

\begin{theorem}
	An empirical theory is convincing iff it has no falsification instances.
\end{theorem}
\begin{proof}
	For all $i \in I, \phi \in {\gleadsto}(\allargs)$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
\end{proof}

@@

Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[i, \phi, 0] \subseteq \allargs$ as $\gargs[i, \phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in 2\N$, define $\gargs[i, \phi, k + 2] = \gargs[i, \phi, k] + [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[i, \phi, k], \ar  \in [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k])}$.
Define $\gargs[i, \phi] = \bigcup_{k \in 2\N} \gargs[i, \phi, k]$, and $\gargs = \cup_{i \in I, \phi \in {\gleadsto}(\allargs)} \gargs[i, \phi]$.

@@

\subsection{Validity}
\begin{definition}[Validity]
	An empirical theory is \emph{valid} iff $\forall \phi \in {\gleadsto}(\allargs): [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
\end{definition}

\subsection{Single-try empirical models}
NB these two conditions should be phrased as properties of a claim. A claim has bl iff for some $k$, …

@@

\begin{definition}[Conv.\ SA]
	$\forall i \in I, \phi \in {\gleadsto}(\allargs), k \in 2\N, \ar \in \gargs[i, \phi, k]: \ar$ $i$-defends $\phi$ ignoring ${\gbeats}(\gargs[i, \phi, k + 2])$.
\end{definition}

@@

\begin{theorem}
	If an empirical theory is Conv.\ SA and has a priori bounded length, and its normative theory satisfies \cref{ax:nocontr,ax:norm}, then it is valid.
\end{theorem}
\begin{proof}
	Consider $i \in I$ and $\phi \in {\gleadsto}(\allargs)$.

@@

Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \nileadstost \phi$.

The following condition mandates that if the arguments used by the theory are not decisive, it knows a reason.
\begin{definition}[Answerability]
	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstost \phi ⇒ [\exists \ar_1' \in {\gbeatsinv}(\ar_0)]$.
\end{definition}

@@

\begin{definition}[Operational validity]
	$\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeats \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
\end{definition}

@@

\subsection{Theorem}
\begin{theorem}
	If a theory is answerable, has bounded length, does not repeat, and is operationally valid, it is valid.
\end{theorem}
\begin{proof}
	Lemma: given $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
	To prove the lemma, let us pick any $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$. 
	We know that $\exists \ar_1 \in \allargs \suchthat (\ar_1, \ar[k]) \nileadstost \phi$. 
	Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeats \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$. 
	Define $\ar[k + 1] = \ar[k] + \ar_2$. This is the element we look for.
	First, $\ar[k + 1] \in \gargs[\phi]$ because $\ar[k + 1] \gbeats \ar_1' \ibeatse[!\phi] \ar[k]$.
	Second, by No repetition, $\ar_2 \notin c(\ar[k])$,
	thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$ (observing that, by definition of $c$, for any $\ar, \ar'$: $c(\ar) \subseteq c(\ar + \ar')$).

	To prove the theorem, given $\phi \in {\gleadsto}(\allargs)$, we need to exhibit an argument $\ar$ such that $\ar \ileadstost \phi$.
	Define a finite sequence $(\ar[0], \ar[1], \ar[2], …)$, starting from $\ar[0] = {\gleadstoinv}(\phi)$, using the lemma, until the condition $\ar[k] \nileadstost \phi$ no longer holds. This condition must turn false after some finite number of steps, because $\card{c(\ar[k])}$ grows at each step, $c(\ar[k]) \subseteq \gargs$ by definition of $c(.)$, and using Bounded length. The last element of the sequence is the argument we look for.
\end{proof}
\commentOC{If playing $\ar_2$ at some stage did not move $i$ and $\ar_1$ still attacks $\ar_0 + \ar_2$, we can say that the model missed answering that step, thus either we choose to give it a second chance (maybe it chose the wrong $\ar_2$ to counter the $\ar_1'$ it believed was relevant, or it needed both $\ar_2$ and $\ar_4$), or we give up in fear of losing our time. Actually, the protocol is that when applying Answerability, we are supposed to pick the $\ar_1'$ that $i$ just was given by another model, thus, if that’s still the same $\ar_1$ as the step before, the model has lost (it can’t map what it’s told to an argument it knows how to answer).}

@@

\subsection{Interpreting Answerability}
At a given stage in operationalizing the protocol, define $f(\ar_0)$ as the arguments that are considered as having a chance to attack $\ar_0$ (without backtracking). Thus, this will not include $\ar_1$ if indeed $\ar_2$ is considered by $i$ as a satisfying answer to $\ar_1$. We can interpret Answerability in the following ways. Strong answ: $\exists \ar_1 \in f(\ar_0) \suchthat \ar_1 \gbeats \ar_0$. Weak answ: $f(\ar_0) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0$. Or suppress Answ and replace Op. val. by Strong op. val.: $\forall \phi \in {\gleadsto}(\allargs), \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.

@@

\begin{definition}[Convincingness]
	$\forall i \in I, \phi \in {\gleadsto}(\allargs), \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
\end{definition}
Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its strenghtening. Similarly, requiring that $S_k ≠ \emptyset$ does not modify the condition (because if some $k$ satisfy the condition with $S_k = \emptyset$, then picking $k' = k-2$ with the same sets $S_j$ also satisfy the condition, and because $S_0 ≠ \emptyset$, this recursion must end with a suitable $k$).

@@

\begin{theorem}
	If an empirical theory is convincing, and its normative theory satisfies the axioms, then it is valid.
\end{theorem}
\begin{proof}
	Consider $i \in I$ and $\phi \in {\gleadsto}(\allargs)$. 
	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\phi$ under protection of $\emptyset$. Therefore, $\ar_k \ileadstosts \phi$. Using \cref{ax:norm}, validity follows.
\end{proof}

>>>>

\section{Additive single-answer empirical theories}
\subsection{Definition}
\commentOC{I leave the definition as is, but for the moment I only consider ${\gleadsto}$, a relation that does not depend on $i$; and I do not use $q(i)$.}
An empirical theory for a normative theory is a tuple $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto[q(i)]} \subseteq (\allargs × \Phi) \cap (\alldargs × \Phi)$, 
${\gbeats} \subseteq \allargs × \allargs$,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range equals ${\gbeatsinv}(\allargs)$, the domain of ${\gbeats}$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: ${\dbeatsinv}(\ar_1)$ is a singleton). 
Define $\df \subseteq \allargs × \alldargs$ as $\df = {\dbeatsinv} \circ {\gbeatsinv}$. 
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \df(\ar)) → \allargs$.
As usual, $\ar + \ard$ means $+(\ar, \ard)$. 
Define $\dfp \subseteq \allargs × \allargs$ as, $\forall \ar \in \allargs$: $\dfp(\ar) = \ar + \df(\ar) = \set{\ar + \ard \suchthat \ard \in \df(\ar)}$.
An empirical theory must satisfy
$\forall \ar \in \gPhi: \exists k \in \N^* \suchthat \dfp^k(\ar) = \emptyset$.

\subsection{Falsifiability}
Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar_0} \subseteq \histend \land \hist \nileadstosti \phi$, and say that $\ar_1$ is an effective attack against $\ar_0$ (from $i$’s perspective).

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [{\dbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatsiinv})](\ar)$. Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$, where $(\dip)^0$ is the identity function over $\allargs$.

@@

\begin{definition}[Convincingness]
	$\forall i \in I, \phi \in \gPhi, \ar \in \gargs[i, \phi]: \ar$ $i$-defends $\phi$.
\end{definition}

A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.

\begin{theorem}
	An empirical theory is convincing iff it has no falsification instances.
\end{theorem}
\begin{proof}
	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land {\gbeatsinv}(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
\end{proof}

\begin{definition}[Validity]
	An empirical theory is \emph{valid} iff $\forall i \in I, \phi \in \gPhi: [\phi \in \iPhi \land ¬\phi \notin \iPhi]$.
\end{definition}

\begin{remark}[TODO]
	$\ar_1 \ibeatsi \ar_0$ only when $\ar_1$ att $\ar_0$ alone (among those planned attacks of $\ar_0$), but $\ar_1$ need not necessarily be at the end of $\hist$. Thus, ${\ibeatsi}$ is a theoretical claim (that other arguments do not matter and that $\ar_1$ is indeed responsible for the change of mind), and $\ar_1 \ibeatsi \ar_0 ⇒ \ar_1 \gbeats \ar_0$.

	Also, a coalition can attack $\ar_0$. Required because could have coal together attacks $\ar_0$ but individual arguments do not. Thus, I am interested in minimal coalitions that attack. For those, the theory must be able to answer with the sum of its replies (in which order?).
	Define $\set{\ar_1, \ar'_1} \ibeatsi \ar_0$. Requires that each argument of the coalition be among the planned attackers; and that sub-coalitions do not attack. This requires a specific answer from the theory, namely, $\ar_0 + \ar_2 + \ar'_2$.

	Define that $\ar_0$ strongly defends $\phi$ iff defense works when using no planned attack, and that $\ar_0 + \ar_2$ works when using only $\ar_1$ and if $\ar_1 \ibeatsi \ar_0$, and that $\ar_0 + \ar_2 + \ar'_2$ works when using both $\ar_1$ and $\ar'_1$ and this is a minimal planned attacking coalition.

	Now, a falsification instance is $\hist$ containing $\ar_1$ and $\ar'_1$, two planned attacks, such that $\ar_2$ alone sometimes fails, $\ar'_2$ alone sometimes fails, and the addition sometimes fails: this proves the theory wrong in all cases, one argument alone attacking or both together being required.

	A coalition could have a synergic effect: theory can reply individually, but fail its collective reply. However, that should not deserve explicit consideration: if individual replies work, and individual argument attacks, then some decisive argument exists.
\end{remark}

I want that s1 attacks-i s0 only when it’s because of s1 (according to the theory). Otherwise, the theory is forced to answer s1, an irrelevant argument. Thus, s1 attacks-e s0 requires that no s1' (planned attack against s0) is used.

Also, everything must be falsifications except when it’s because of s1 i-attacking s0 (in which case the theory commits to answer). Thus, if two planned attacks are used, this is a falsification instance? No, because the theory commits to answer each one separately. Thus, if two planned attacks are used AND individual ones do not i-attack, then it is a falsification instance. Also, if (s1, s0, s0) leads to not phi, and not (s0, s1, s0), then this is a falsification instance.

Convincingness must happen exactly when there is no falsification instance. Thus, ar i-defends phi when all dangerous histories are answered to by ar and when two planned attacks i-attack, some individual one i-attacks and when (s1, s0, s0) leads to not phi, then (s0, s1, s0) leads to not phi.

Hence, the dangerous histories are those such that no reordering lead to $\set{\ar_1, \ar_0} = \histend$ for some $\ar_1$ that is a planned, effective attack. (involve no planned-attack or multiple irreducible planned attacks or an attack that happens only with a strange ordering).
Well, that’s not great: to know whether an instance falsifies, we’d need to ensure, for each reordering of planned attacks, that they are non effective attacks, which is basically impossible. NO suffices to exhibit some history hist' with ar1, ar0 at end and leading to phi.

Thus, falsification: hist, ar1=> hist', ar1' => hist'', where hist uses ar1 and ar1' (which are all the planned attacks in hist) and hist' ends with ar1, ar0, hist => notphi, hist' => phi, and so on.

%Rather keep falsification instances simple, and enlarge the situations that the theory commits to answer. If some history combine ar1 and ar1' and lead to not phi, the theory must answer either ar1 or ar1' (it can choose => if ar1, ar0 in histend lead to not phi, it must answer ar1; if ar1' etc.; and if none, then it has lost). Thus falsification happens when both ar1 and ar1' are used and some some hist, ar1 does not attack ar0 and for some hist, ar1' does not attack ar0. This can be checked. And about (s1, s0, s0) (with s1 not planned): this is a falsification instance. Define it as: no planned attack is used AND s1 in hist AND s0 in histend.

\begin{theorem}
	A normatively adequate and convincing empirical theory is valid.
\end{theorem}
\begin{proof}
	\commentOC{This might be false. Consider ${\gbeats} = \set{(\ar_1, \ar_0)}, {\dbeats} = \set{(\ar_2, \ar_1)}, (\ar_1, \ar_0, \ar'_1) \ileadstoi ¬\phi$. There is no decisive argument in $\gargs[i, \phi]$ as $\ar'_1 \ibeatsi \ar_0$, but no falsification instance as $\hist = (\ar_1, \ar_0, \ar'_1)$ includes $\ar_1$. In such a situation, $\ar_1$ should be considered as attacking $\ar_0$, as (from the model pov) it is $\ar_1$ which makes $i$ fail to adopt $\phi$.}

	For all $i \in I, \phi \in \gPhi$, suffices to show that for some $\ar \in \gargs[i, \phi]$, $\ar \ileadstosti \phi$.

	Consider any $\ar_0 \gleadsto \phi$.
	By definition of $\dip$, $\forall k \in \N^*: (\dip)^k(\ar_0) \subseteq \dfp^k(\ar_0)$.
	By definition of an empirical theory, $\exists k \in \N^* \suchthat \dfp^k(\ar_0) = \emptyset$. 
	Therefore, $\exists k \in \N^* \suchthat (\dip)^k(\ar_0) = \emptyset$. 
	Define $l = \min \set{k \in \N^* \suchthat (\dip)^k(\ar_0) = \emptyset}$.

	Consider any $\ar \in (\dip)^{l-1}(\ar_0)$, and let us show that $\ar \ileadstosti \phi$.

	If $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatsi \ar$, then $\exists \hist \in \allhist \suchthat \set{\ar_1, \ar} \subseteq \histend \land \hist \nileadstosti \phi$, and a falsification instance $(i, \phi, \hist)$ is found, which contradicts convincingness. \commentOC{Unless $\hist$ contains some planned attack!}
	Therefore, no $\ar_1 \ibeatsi \ar$.

	Because $\ar \in \gargs[i, \phi]$, $\ar$ $i$-defends $\phi$. Furthermore, ${\gbeatsinv}(\ar) = \emptyset$, because by definition of an empirical theory, if $\ar_1 \gbeats \ar$, then $\ar_2 \dbeats \ar_1$, which contradicts $\dip$ NO!
\end{proof}

@@

Given $\phi \in \gPhi$, define $\gargs[i, \phi, 0] \subseteq \allargs$ as $\gargs[i, \phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in 2\N$, define $\gargs[i, \phi, k + 2] = \gargs[i, \phi, k] + [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[i, \phi, k], \ar  \in [{\gbeatsinv} \circ ({\gbeatsinv} \cap {\ibeatseinv[!\phi]})](\gargs[i, \phi, k])}$.
Define $\gargs[i, \phi] = \bigcup_{k \in 2\N} \gargs[i, \phi, k]$, and $\gargs = \cup_{i \in I, \phi \in \gPhi} \gargs[i, \phi]$.

@@

\subsection{Validity}
\subsection{Single-try empirical models}
NB these two conditions should be phrased as properties of a claim. A claim has bl iff for some $k$, …

@@

\begin{definition}[Conv.\ SA]
	$\forall i \in I, \phi \in \gPhi, k \in 2\N, \ar \in \gargs[i, \phi, k]: \ar$ $i$-defends $\phi$ ignoring ${\gbeats}(\gargs[i, \phi, k + 2])$.
\end{definition}

@@

\begin{theorem}
	If an empirical theory is Conv.\ SA and has a priori bounded length, and its normative theory satisfies \cref{ax:nocontr,ax:norm}, then it is valid.
\end{theorem}
\begin{proof}
	Consider $i \in I$ and $\phi \in \gPhi$.

@@

Given $\phi \in \gPhi$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \nileadstost \phi$.

The following condition mandates that if the arguments used by the theory are not decisive, it knows a reason.
\begin{definition}[Answerability]
	$\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \nileadstost \phi ⇒ [\exists \ar_1' \in {\gbeatsinv}(\ar_0)]$.
\end{definition}

@@

\begin{definition}[Operational validity]
	$\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: [\ar_1 \gbeats \ar_0 \land (\ar_1, \ar_0) \nileadstost \phi] ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.
\end{definition}

@@

\subsection{Theorem}
\begin{theorem}
	If a theory is answerable, has bounded length, does not repeat, and is operationally valid, it is valid.
\end{theorem}
\begin{proof}
	Lemma: given $\phi \in \gPhi$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
	To prove the lemma, let us pick any $\phi \in \gPhi$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$. 
	We know that $\exists \ar_1 \in \allargs \suchthat (\ar_1, \ar[k]) \nileadstost \phi$. 
	Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeats \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$. 
	Define $\ar[k + 1] = \ar[k] + \ar_2$. This is the element we look for.
	First, $\ar[k + 1] \in \gargs[\phi]$ because $\ar[k + 1] \gbeats \ar_1' \ibeatse[!\phi] \ar[k]$.
	Second, by No repetition, $\ar_2 \notin c(\ar[k])$,
	thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$ (observing that, by definition of $c$, for any $\ar, \ar'$: $c(\ar) \subseteq c(\ar + \ar')$).

	To prove the theorem, given $\phi \in \gPhi$, we need to exhibit an argument $\ar$ such that $\ar \ileadstost \phi$.
	Define a finite sequence $(\ar[0], \ar[1], \ar[2], …)$, starting from $\ar[0] = {\gleadstoinv}(\phi)$, using the lemma, until the condition $\ar[k] \nileadstost \phi$ no longer holds. This condition must turn false after some finite number of steps, because $\card{c(\ar[k])}$ grows at each step, $c(\ar[k]) \subseteq \gargs$ by definition of $c(.)$, and using Bounded length. The last element of the sequence is the argument we look for.
\end{proof}
\commentOC{If playing $\ar_2$ at some stage did not move $i$ and $\ar_1$ still attacks $\ar_0 + \ar_2$, we can say that the model missed answering that step, thus either we choose to give it a second chance (maybe it chose the wrong $\ar_2$ to counter the $\ar_1'$ it believed was relevant, or it needed both $\ar_2$ and $\ar_4$), or we give up in fear of losing our time. Actually, the protocol is that when applying Answerability, we are supposed to pick the $\ar_1'$ that $i$ just was given by another model, thus, if that’s still the same $\ar_1$ as the step before, the model has lost (it can’t map what it’s told to an argument it knows how to answer).}

@@

\subsection{Interpreting Answerability}
At a given stage in operationalizing the protocol, define $f(\ar_0)$ as the arguments that are considered as having a chance to attack $\ar_0$ (without backtracking). Thus, this will not include $\ar_1$ if indeed $\ar_2$ is considered by $i$ as a satisfying answer to $\ar_1$. We can interpret Answerability in the following ways. Strong answ: $\exists \ar_1 \in f(\ar_0) \suchthat \ar_1 \gbeats \ar_0$. Weak answ: $f(\ar_0) ≠ \emptyset ⇒ \exists \ar_1' \suchthat \ar_1' \gbeats \ar_0$. Or suppress Answ and replace Op. val. by Strong op. val.: $\forall \phi \in \gPhi, \ar_0 \in \gargs[\phi], \ar_1 \in \allargs: (\ar_1, \ar_0) \ileadstoe ¬\phi ⇒ \exists \ar_2 \in {\gbeatsinv}(\ar_1)$.

@@

\begin{definition}[Convincingness]
	$\forall i \in I, \phi \in \gPhi, \exists k \in 2\N$ and a finite sequence $(\args_j)_{j \in 2\N, j ≤ k} \suchthat \emptyset ≠ \args_0 \subseteq {\gleadstoinv}(\phi)$ and $\forall j \in 2\N, j ≤ k, \forall \ar_j \in S_j: \ar_j$ $i$-defends $\phi$ under protection of $S_{j + 2}$ (defining $S_{k + 2} = \emptyset$) and $S_j \subseteq \cup_{\ar_{j - 2} \in \args_{j - 2}, \ar_{j - 1} \in \allargs} f(\ar_{j - 1}, \ar_{j - 2})$.
\end{definition}
Note that requiring that $\args_0$ be a singleton does not modify the condition, in the sense that any theory satisfying the condition also satisfies its strenghtening. Similarly, requiring that $S_k ≠ \emptyset$ does not modify the condition (because if some $k$ satisfy the condition with $S_k = \emptyset$, then picking $k' = k-2$ with the same sets $S_j$ also satisfy the condition, and because $S_0 ≠ \emptyset$, this recursion must end with a suitable $k$).

@@

\begin{theorem}
	If an empirical theory is convincing, and its normative theory satisfies the axioms, then it is valid.
\end{theorem}
\begin{proof}
	Consider $i \in I$ and $\phi \in \gPhi$. 
	By hypothesis, $\exists k$ such that some $\ar_k \in \args_k$ defends $\phi$ under protection of $\emptyset$. Therefore, $\ar_k \ileadstosts \phi$. Using \cref{ax:norm}, validity follows.
\end{proof}
